Tennis

### 2019-12-18 PaperDraft.Rmd
Added ToC

@@

### Introduction

@@

### Motivation

@@

### Methods

@@

### Reproducability

@@

```{r, echo=FALSE, message=F, warning=F, fig.pos="H"}
W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") + 
  ylab("Number of Times Won") +
  ggtitle("Figure 1",
          subtitle = "2002 Women's US Open")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
mOpen <- read_csv('2002 US Open- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T2)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("Proportion of Times Won") +
  ggtitle("Figure 2",
          subtitle = "2002 Men's US Open")

@@

kable(Wimb2002, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2002 Wimbledon Tournament
")%>%
          kable_styling(latex_options = "scale_down")

```
```{r, message=F, warning=F, fig.pos="H"}
wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 3',
          subtitle = "2002 Women's Wimbledon")
```
```{r, message=F, warning=F, fig.pos="H"}
mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 4 ',
          subtitle = "2002 Men's Wimbledon")
```

### Extension

@@

Tab<-cbind(Tab1, Tab2)
kable(Tab, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2019 Wimbledon Tournament
")%>%
          kable_styling(latex_options = "scale_down")

@@

```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 5',
          subtitle = "2019 Women's Wimbledon")
```

```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}

@@

ggplot(data.frame(T5)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle('Figure 6',
          subtitle = "2002 Men's Wimbledon")
```

### Conclusions

### Limitations

@@

### Bibliography

>>>>

\newpage
\tableofcontents
\listoffigures
\listoftables
\newpage

@@

# Introduction

@@

# Motivation

@@

# Methods

@@

# Reproducability

@@

```{r, echo=FALSE, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's US Open"}
W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") + 
  ylab("Number of Times Won") +
  ggtitle("2002 Women's US Open")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap = "2002 Men's US Open"}
mOpen <- read_csv('2002 US Open- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T2)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("Proportion of Times Won") +
  ggtitle("2002 Men's US Open")

@@

kable(Wimb2002, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2002 Wimbledon Tournament
")%>%
          kable_styling(full_width = T)

```
```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's Wimbledon"}
wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T3)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle("2002 Women's Wimbledon")
```
```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Men's Wimbledon"}
mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
  filter(!is.na(Name)) %>%
  mutate(pRally = NA)

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle("2002 Men's Wimbledon")
```

# Extension

@@

Tab<-cbind(Tab1, Tab2)
kable(Tab, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2019 Wimbledon Tournament
")%>%
          kable_styling(full_width = T)

@@

```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Women's Wimbledon"}

@@

ggplot(data.frame(T4)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle("2019 Women's Wimbledon")
```

```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Men's Wimbledon"}

@@

ggplot(data.frame(T5)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab('Players') +
  ylab('Proportion of Times Won') +
  ggtitle("2019 Men's Wimbledon")
```

# Conclusions

# Limitations

@@

# References
